Compositional equivalences based on Open pNets

### 2020-03-10 2016-Weak-FH-Bisim/WeakBisim.tex
def subst, et (beta)v

\author{Eric Madelaine}
\address{INRIA Sophia Antipolis M\'edit\'erann\'ee, BP 93, 06902 Sophia Antipolis, France}
%\date{}                                           % Activate to display a given date or no date
\author{Rab\'ea Ameur-Boulifa}
                          % Activate to display a given date or no date

@@

Note that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = t\subst{\Post}\subst{\Post'}$

@@

By definition, one weak open transition contains  several open transitions, where  each open transition can require an observable action from a given hole, the same hole might have to emit several observable actions for a single weak open transition to occur. 
Consequently, for a weak open transition to trigger, a list of actions from a given hole might be required.

Thus, we let $\gamma$ range over lists of action terms and use $\dotcup$ as the union operator that appends lists of action terms: given two  lists of action terms  $\gamma\dotcup\gamma '$ concatenates the two lists. The operation is lifted to indexed sets of lists:  $\set {\gamma_1}\dotcup \set {\gamma_2}$ is an indexed set of lists such that, at each index $i$, $\set {\gamma_1}\dotcup \set {\gamma_2}$ concatenates the list of  actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$\footnote{One of the two lists is empty when $i\not \in \dom(\set{\gamma_1})$ or $i\not \in \dom(\set{\gamma_2})$ .}. $[a]$ denotes a list with a single element.

@@

>>>>

\author{Eric Madelaine}
\address{INRIA Sophia Antipolis M\'edit\'erann\'ee, UCA, BP 93, 06902 Sophia Antipolis, France}
\email{eric.madelaine@inria.fr}
%\date{}                                           % Activate to display a given date or no date
\author{Rab\'ea Ameur-Boulifa}
                          % Activate to display a given date or no date

@@

Note that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = (t\subst{\Post})\subst{\Post'}$.\\
\ERIC{J'ai un probleme ici... quand $Post'$ agit sur des vars de $t$ qui ne sont pas substitutees par $Post$, alors les 2 defs de $\shortotimes$ ci-dessus ne sont pas equivalentes:}\\
$F(x,z)(\subst{x\gets z}\shortotimes\subst{z\gets 1})=F(x,z)(\subst{x\gets 1})=F(1,z)$\\
\ERIC{Alors que}\\
$(F(x,z)\subst{x\gets z})\subst{z\gets 1})=F(z,z)\subst{z\gets 1}=F(1,1)$

\ERIC{Une definition plus correcte serait peut-etre:}\\
$(x_{k}\gets e_{k})^{k\in K}\shortotimes (x_{k'}\gets e_{k'})^{k'\in K'} =  
(x_{k}\gets e_{k}\subst{(x_{k'}\gets e_{k'})^{k'\in K'}})^{k\in K} \cup (x_k\gets e_k)^{k\in K'\backslash K}$

@@

By definition, one weak open transition contains  several open transitions, where  each open transition can require an observable action from a given hole, the same hole might have to emit several observable actions for a single weak open transition to occur. 
Consequently, for a weak open transition to trigger, a sequence of actions from a given hole may be required.

\TODO{Check, nouvelle formulation, Eric}
Thus, we let $\gamma$ range over lists of action terms and use $\dotcup$ as the union operator that appends lists of action terms: given two  lists of action terms  $\gamma\dotcup\gamma '$ concatenates the two lists. The operation is lifted to indexed sets of lists:  $\set {\gamma_1}\dotcup \set {\gamma_2}$ is an indexed set of lists such that, at each index $i$, $\set {\gamma_1}\dotcup \set {\gamma_2}$ concatenates the list of  actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$. $[a]$ denotes a list with a single element.

\ERIC{Thus, we let $\gamma$ range over sequences of action terms and use $\dotcup$ as the concatenation operator that appends sequences of action terms: given two sequences of action terms  $\gamma\dotcup\gamma '$ concatenates the two lists. The operation is lifted to indexed sets of sequences:  $\set {\gamma_1}\dotcup \set {\gamma_2}$ is an indexed set such that, at each index $i$, $\set {\gamma_1}\dotcup \set {\gamma_2}$ concatenates the sequences of actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$\footnote{One of the two sequences is empty when $i\not \in \dom(\set{\gamma_1})$ or $i\not \in \dom(\set{\gamma_2})$ .}. $[a]$ denotes a sequence with a single element.}

@@

\ERIC{As required actions are now sequences of observable actions, we need an operator to build them from set of (single) hole actions that occur in open transitions.
Thus we define $\vis{\set\beta}$ as the mapping $\set\beta$  with only observable actions of the holes in $I$, but where each element is either empty or a list of length 1:
 \[\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}\text{ where }I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}\]}

\ERIC{As an example the $\vis{\set\beta}$ built from the transition $OT_1$ in page \pageref{OT:SimpleProt} is $\texttt{P}\mapsto [\texttt{p-send(m)}]$. Remark that in our simple example no $\tau$ transition involves any visible action from a hole, so we have no $\beta$ sequences of length longer than 1 in the weak automaton.}
